### 2009-10-30 doc/manuals/chelonia/arc-storage-manual.tex
fixing the manual
updating the chelonia manual

\begin{verbatim}
$ sudo /usr/local/sbin/arched -c /etc/arc/storage_service.xml -f
\end{verbatim}

@@

\begin{verbatim}
<Service name="pythonservice" id="bartender">
    <ClassName>storage.bartender.bartender.BartenderService</ClassName>
    <LibrarianURL>[...]</LibrarianURL>
    <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
    <GatewayClass>storage.bartender.gateway.gateway.Gateway</GatewayClass>
    <GatewayCfg>
        <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
        <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
    </GatewayCfg>
    <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
</Service>
\end{verbatim}

@@

ARC has its own multi-protocol storage client tools which provide a unified way to access different kind of storage. For all the supported types there is a DMC module. For Chelonia, the ARC DMC module is used. If it is compiled and installed, then you can use the \verb!arcls!, \verb!arccp!, \verb!arcrm!, etc. tools with the \verb!arc://! protocol to access the ARC storage system. You can specify the URL of the Bartender with the \verb!BartenderURL! URL option, or you can have a Bartender URL configured in the \verb!client.xml! user config.

\begin{verbatim}
$ arcls arc:///
$ arccp orange arc:///orange
$ arcls arc:///
orange
$ arcls arc:///?BartenderURL=https://storage2:60006/Bartender
orange
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.56 seconds.
'/': collection
  orange <file>
$ chelonia makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 2.38 seconds.
Creating collection '/fruits': done
$ arccp arc:///orange arc:///fruits/orange
$ arcls arc:///
orange
fruits
$ arcls arc:///fruits
orange
$ arccp arc:///orange /tmp/orange
$ cat /tmp/orange 
orange
$ arcrm arc:///orange
$ arcls arc:///
fruits
\end{verbatim}

@@

\item Set up \verb!~/.arc/client.xml!:

\begin{verbatim}
$ cat ~/.arc/client.xml 
<ArcConfig>
  <KeyPath>/home/<username>/.arc/userkey.pem</KeyPath>
  <CertificatePath>/home/<username>/.arc/usercert.pem</CertificatePath>
  <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
  <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
</ArcConfig>
\end{verbatim}

\item Create a mountpoint and mount arcfs.py:
\begin{verbatim}
   $ pwd
   /home/me/arc
   $ ln -s arc1/src/services/storage/fuse/arcfs.py arcfs.py
   $ mkdir mnt
   $ python arcfs.py ./mnt 
\end{verbatim}
This mounts ARCFS in \verb!/home/me/arc/mnt!, creates directory
\verb!/home/me/arc/fuse_transfer! and a log file
\verb!/home/me/arc/arcfsmessages!.

@@

Now, remounting the system, everything should still be there:
\begin{verbatim}
   $ python arcfs.py ./mnt

>>>>

\begin{verbatim}
$ sudo /usr/sbin/arched -i /etc/arc/chelonia1.ini -f
\end{verbatim}

@@

\begin{verbatim}
[bartender]
endpoint=https://chelonia3.knowarc.eu:60003/Bartender
proxystore=/var/spool/arc/proxy_store
\end{verbatim}

@@

ARC has its own multi-protocol storage client tools which provide a
unified way to access different kind of storage. For all the supported
types there is a DMC module. For Chelonia, the ARC DMC module is
used. If it is compiled and installed, then you can use the
\verb!arcls!, \verb!arccp!, \verb!arcrm!, etc. tools with the
\verb!arc://! protocol to access the ARC storage system. You can
specify the URL of the Bartender with the \verb!BartenderURL! URL
option, or you can have a Bartender URL configured in the
\verb!client.ini! user config by adding an entry \verb!bartender!:

\begin{verbatim}
bartender= https://chelonia1/Bar https://chelonia2/Bar https://chelonia3/Bar
\end{verbatim}

If the \verb!client.ini! is not in the default path (for Linux,
\verb!$HOME/.arc/client.conf!), you need to specify the path to the
configuration file with the \verb!-z! option.

% todo: make arc dmc look up isis

\begin{verbatim}
$ arcls arc:///
$ arccp orange arc:///orange
$ arcls arc:///
orange
$ arcls arc:///?BartenderURL=https://chelonia1.knowarc.eu:60001/Bartender
orange
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.56 seconds.
'/': collection
  orange <file>
$ chelonia makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 2.38 seconds.
Creating collection '/fruits': done
$ arccp arc:///orange arc:///fruits/orange
$ arcls arc:///
orange
fruits
$ arcls arc:///fruits
orange
$ arccp arc:///orange /tmp/orange
$ cat /tmp/orange 
orange
$ arcrm arc:///orange
$ arcls arc:///
fruits
\end{verbatim}

@@

\item Make sure \verb!bartender! is set in
  \verb!$HOME/.arc/client.conf!:
\begin{verbatim}
$ grep bartender ~/.arc/client.conf 
bartender= https://chelonia1.knowarc.eu:60001/Bartender
\end{verbatim}

\item Create a mountpoint and mount arcfs:
\begin{verbatim}
   $ pwd
   /home/me/arc
   $ mkdir mnt
   $ arcfs ./mnt 
\end{verbatim}
This mounts ARCFS in \verb!/home/me/arc/mnt!, creates directory
\verb!/home/me/arc/fuse_transfer! and a log file
\verb!/home/me/arc/arcfsmessages!.

@@

Now, remounting the system, everything should still be there:
\begin{verbatim}
   $ arcfs ./mnt
